How kids code and how we know it:\\An exploratory study in the Scratch project repository

### 2016-04-18 Paper/paper.tex
Added section summary box

>>>>

\noindent
\fbox{
	\begin{minipage}{0.46\textwidth}
		\emph{RQ1: The majority of Scratch projects are small and simple; 75\% of the projects have up to 5 sprites, 12 scripts, 76 lines of code and no decision points. Most code is written in sprites. Few projects (7.7\%) use procedures, but they use them a lot. There exist surprisingly large and complex projects.}
	\end{minipage}}
